---
title: "Data Cleanup Vecdyn Bulk Uploader"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
# install.packages("tidyverse")
# install.packages("readr")
# install.packages("plyr")
# install.packages("scales")
library(tidyverse)
library(readr)
library(plyr)
library(scales)
library(lubridate)
library(stringr)
library(stringi)
library(magrittr)
```


### Template 

Note that all data frame fields are created in character format,  you'll need to convert them to the correct formats at a later stage. You can use this data frame as a guide to help you convert your data-set to the VecDyn format. You can either import data into into the data frames below or just rename the field names of the data-set you are working on.  However,  you need to make sure all the columns are in the correct order as below,  even if your data set is missing certain fields. In this case you need to create them  and leave them blank. 

```{r}
vecdyn_bulk_upload_template  <- data.frame(title=character(), 
                             # collection_author=character(), note that for bulk uploads we do not include the collection author
                             dataset_citation=character(),
                             publication_citation = character(),
                             description = character(),
                             url = character(),
                             contact_name=character(),
                             contact_affiliation=character(),
                             email=character(),
                             orcid=character(),
                             dataset_license=character(),
                             project_identifier=character(),
                             publication_status=character(),
                             taxon = character(),
                             location_description = character(),
                             study_collection_area = character(),
                             geo_datum = character(),
                             gps_obfuscation_info = character(),
                             species_id_method = character(),
                             study_design = character(),
                             sampling_strategy = character(),
                             sampling_method = character(),
                             sampling_protocol = character(),
                             measurement_unit = character(),
                             value_transform = character(),
                              sample_start_date = character(),
                             sample_start_time = character(),
                             sample_end_date =  character(),
                             sample_end_time = character(),
                             sample_value = character(),
                             sample_sex = character(),
                             sample_stage = character(),
                             sample_location = character(),
                             sample_collection_area = character(),
                             sample_lat_dd = character(),
                             sample_long_dd = character(),
                             sample_environment = character(),
                             additional_location_info = character(),
                             additional_sample_info = character(),
                             sample_name = character(),
                             stringsAsFactors=FALSE)
#write.csv(VecDyn_template, file = "VecDyn_template.csv", row.names = FALSE)
                             
```


## VectorBase Bulk Data Compilation

```{r}
library(readr)
vectorbasepublicationinfo <- read_csv("files/vectorbase/VectorBasePublicationInfo.csv", 
    col_types = cols(X12 = col_character(), 
        dev_stages_ss = col_character(), 
        tags_ss = col_character()))
View(VectorBasePublicationInfo)
```


```{r}
vectorbite <- read_csv("files/vectorbase/abundance-2019-02.csv", 
     col_types = cols(`Collection duration (days)` = col_character(), 
         `Specimens collected` = col_character()))
```


```{r}
head(vectorbite)
```


```{r}

colnames(vectorbasepublicationinfo)

```

```{r}

vectorbite <-dplyr::inner_join(vectorbite, vectorbasepublicationinfo, by = c("Projects" = "accession"))

```

```{r}
vectorbite <- dplyr::select(vectorbite, -`Sample ID`, -Label, -`Collection ID`, -'X12.x', -'tags_ss', -"exp_citations_ss", -'licenses_ss', -'dev_stages_ss')
```


```{r}

# filter by date year month

dataBySpFem <- 
  vectorbite %<>%
  dplyr::filter(nchar('collection date range' < 8))

``` 




```{r}


vectorbite <- filter(vectorbite, Projects %in% c('VBP0000281', 'VBP0000284', 'VBP0000332', 'VBP0000386', 'VBP0000229','VBP0000317', 'VBP0000333'))
```
 
```{r}
colnames(vectorbite)
```

```{r}

vectorbite <- separate(vectorbite, Coordinates, into = c("sample_lat_dd", "sample_long_dd"), sep = ",")


```

 
```{r}

title <- vectorbite$label
dataset_citation <- vectorbite$Citations
description <- vectorbite$description
contact_name <- vectorbite$authors
dataset_license <- vectorbite$`Usage license`
taxon <- vectorbite$Species
location_description <- vectorbite$Locations
sampling_protocol <- vectorbite$`Collection protocols`
study_design <- vectorbite$study_designs
sampling_method <- vectorbite$Attractants
sample_end_date <- vectorbite$`Collection date range`
sample_value <- vectorbite$`Specimens collected`
sample_sex <- vectorbite$Sex
sample_stage <- vectorbite$`Developmental stage`
sample_lat_dd <- vectorbite$sample_lat_dd
sample_long_dd <- vectorbite$sample_long_dd


```


```{r}

a <- cbind(title, dataset_citation, description, contact_name, dataset_license, taxon, sample_value, sample_sex, sample_stage, sample_end_date, sample_lat_dd, sample_long_dd, location_description, sampling_method, sampling_protocol)

a <- data.frame(a, stringsAsFactors=FALSE)

vecdyn_vectorbase_bulk_upload_dataset  <- rbind.fill(vecdyn_bulk_upload_template , a)


```


```{r}
vecdyn_vectorbase_bulk_upload_dataset <- 
  vecdyn_vectorbase_bulk_upload_dataset %>%
  dplyr::mutate(sample_end_date = as.Date(as.character(sample_end_date, format = "%Y/%m/%d"))) %>%
  dplyr::mutate(sample_value = as.numeric(sample_value))


```


```{r}
vecdyn_vectorbase_bulk_upload_dataset <- 
  vecdyn_vectorbase_bulk_upload_dataset %>%
  filter(taxon %in% c('Anopheles perplexens', 'Aedes atlanticus', 'Culex pipiens'))


```


```{r}


write.csv(vecdyn_vectorbase_bulk_upload_dataset, file = "vecdyn_vectorbase_bulk_upload_dataset.csv", row.names = FALSE, na = "")

```

```{r}

vecdyn_vectorbase_bulk_upload_dataset  %>%
  select(dataset_license)  %>%
  distinct()
```

